### 2020-07-17 paper/conclusion.tex
After Osama's changes

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

>>>>

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

### 2020-07-17 paper/introduction.tex
After Osama's changes

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity} since
the MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case.
The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
core reactivity when the core heats up, thus, graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency. In most MSR design concepts, a freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL must be large (up to $8.1$\%) for many refueling scenarios
\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
Additionally, during burnup, online reprocessing and refueling system as long-term reactivity control in
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
however, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the absorption ability under irradiation, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and
absorb neutrons mainly through (n,$\gamma$) reactions
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The SD-TMSR with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new, 
rapid reactivity control system based on control rods in the SD-TMSR to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six absorbing material options are considered in the context of the 
neutronics and safety parameters in the SD-TMSR. We 
focus on control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin, and shadowing 
effects at steady state calculation.

@@

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole}
due to its potential advantages, for example, thorium fuel utilization, small waste production, and ability to use spent fuel.
However, this technology has difficulties including safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of
the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case.
The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
core reactivity when the core heats up, thus MSRs have negative total temperature coefficient of reactivity 
\cite{nuttin2005potential}.
MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency. In some MSR design concepts, a freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Robertson (1971) assumed small excess reactivity for \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel, thus only 2 control (graphite) rods for adjusting reactivity and 2 safety (B$_4$C) rods for emergency shutdown were suggested \cite{robertson_conceptual_1971}. However, scientists are concerned about $^{233}$U supply, since it does not exist anywhere. Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required. Betzler \emph{et al.} (2017) also reported large excess reactivity to operate Transatomic Power Molten Salt Reactor (TAP MSR) for a long time \cite{betzler2017assessment}. Additionally, Rykhlevskii \emph{et al.} (2019) studied the fuel cycle performance for various designs of the \gls{MSFR}. For MSFRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}. Recent studies on MSRs showed that the excess reactivity 
at the BOL may vary from 1.2 \% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1 \% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.

The online reprocessing and refueling system is designed to operate as long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its clones. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable procedure to control the reactor is to insert or withdraw control rods made of material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, Nuclear Regulatory Commission (NRC) regulation requires that one of the reactivity control systems use control rods \cite{nuclear1987standard}.

Boron carbide (B$_4$C) is a commonly used material for the control rods; 
however, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the absorption ability under irradiation, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and
absorb neutrons mainly through (n,$\gamma$) reactions
\cite{guo2019optimized}.

The SD-TMSR with a thermal power of 2,250 MW$_{th}$ 
\cite{li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020Strategies,li_optimization_2018}. However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity}. Therefore, the main objective of our study is to introduce a new, 
rapid reactivity control system based on control rods in the SD-TMSR to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six absorbing material options are considered in the context of the 
neutronics and safety parameters in the SD-TMSR. We 
focus on control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin, and shadowing 
effects at steady state calculation.

@@

The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors. Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those of startup. The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing. Therefore, the worth of the control rods should be corresponding to the reprocessing scheme; that is, the rate of extraction and addition of elements. However, the present work focuses on the steady state calculations (i.e. without burnup).

### 2020-07-17 paper/methods.tex
After Osama's changes

The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the SD-TMSR core geometry
\cite{li_optimization_2018,ashraf2020whole}. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
		Fuel volume, m$^3$  &	52.9 \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		B$_4$C density, g/cm$^3$  &  2.54 \\
		HfB$_2$ density, g/cm$^3$  &  10.5 \\
		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
		SiC density, g/cm$^3$  & 3.21 \\
		AIM1 cladding density, g/cm$^3$  & 7.987 \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Radius (inner fuel channel), cm							& 3.5  \\
		Radius (outer fuel channel), cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\

@@

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.04-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement.
All densities of rod materials are listed in
Table~\ref{tab:table1}.

@@

Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, we propose an original distribution as a starting point of this analysis. We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods can move together as one group (cluster). Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{$XZ$ section of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

@@

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full core of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrate whole-core 
runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and
statistical error in $k_{eff}$ of $\leq$ $25$ 
$pcm$.

@@

The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}.

@@

The shutdown margin (SDM) is the amount of reactivity by which a full reactor core is subcritical from a given state. The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity:

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod impacts the reactivity worth of another control rod in 
the surroundings. 
The insertion of a CR depresses the neutron flux
in its vicinity and makes the curvature of the neutron flux greater. The gradient
of the neutron flux will contrarily increase at a radial distance. The CRs, distributed in the core,
will distort the neutron flux around each other and will impact the reactivity worth.
The term ``shadowing effect" has been used to describe this \cite{oka2014nuclear}.
The shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D), CR locations, and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear,girardin2007control}.

The amplification factor of the i$^{th}$ CR (A$_{CRi}$) helps to evaluate the shadowing effects between CR clusters. The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:

>>>>

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
		Fuel volume, m$^3$  &	52.9 \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Radius (inner fuel channel), cm							& 3.5  \\
		Radius (outer fuel channel), cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\

@@

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{Radius.png}
	\caption{The change of the effective multiplication factor with the radius of the B$_4$C control rod.}
	\label{fig:Radius}
\end{figure}

The assessment of the optimal absorber radius should be an important consideration. If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod. As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius. However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
From the obtained results, the control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement.
All densities of rod materials are listed in
Table~\ref{tab:table111}.

\begin{table}
	\caption{The densities of the absorbing materials.}
	\vspace{0.05in}
	\begin{center}	
		\begin{tabular}{|l | r|}  %[!ht]
			%%	\begin{tabularx}{\textwidth}{l | r}
			\hline
			Absorbers & Density [g/cm$^3$]\\
			\hline
			B$_4$C   &  2.54 \\
			HfB$_2$   &  10.5 \\
			HfH$_{1.62}$  &  11.4 \\
			Gd$_2$O$_3$   &  7.04 \\
			Eu$_2$O$_3$  &  7.38 \\
			SiC   & 3.21 \\
			AIM1 cladding   & 7.987 \\
			\hline
			%	\end{tabularx}
		\end{tabular}
		\label{tab:table111}
	\end{center}
\end{table}

%From the figure it can be seen that in the outer region of the B4C
%absorber, the flux is degraded rapidly, but in the region between 0 and 2 cm there is almost no change of the neutron flux. This phenomenon can be explained by the geometry self-shielding of the neutron flux. Due to absorption of low energy neutrons at the outside region ofthe absorber pin, the radius ofthe investigated pin is significantly larger than the penetration distance of the neutrons in the absorber. Therefore, the 10B atoms in the central part of the pin have no reasonable chance for neutron capture. Based
%
%
%On the basis of the obtained results the 5 ring configuration was selected for further
%ness (low self-shielding) and simplicity. On the basis of the obtained results the 5 ring configuration was selected for further
%analyses.
%
%This CR design consists of 61 absorber pins. Using Eq. (6) the radius of the absorber pins was calculated to 0.574 cm.
%
%In terms of neutronics, we an appropriate way to find the optimal pin radius could be the investigation of the neutron penetration distance, performed on a simple absorber pin.
%
%A single-pin design is a semi 1D approach preventing any interference caused by the self-shielding or geometrical influences of the surrounding absorber pins.

@@

Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, we propose an original distribution as a starting point of this analysis. We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods can move together as one group (cluster). Figure~\ref{fig:graphite_elemen} demonstrates the plan view of the graphite element with the control rods. We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
%\begin{figure}[t!]  % replace 't' with 'b' to \centering
%	\centering
%	\hspace{+0.65in}
%	\includegraphics[width=\textwidth]{graphite_element1.png}
%	\caption{$XZ$ section of graphite element with control rods.}
%	\label{fig:graphite_elemen1}
%\end{figure}

@@

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full core of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrated in this study were obtained after full-core calculations simulating 25$\times$10$^6$ active neutron histories per cycle. Simulations consisted in 500 active cycles of 5$\times$10$^4$ neutrons subdivided in 8 parallel tasks. Each simulation skipped 50 inactive cycles before beginning active tallies to allow for the convergence of the fission source distribution. Convergence has been checked through the fission source entropy. The statistical error in $k_{eff}$ was $\leq$ $25$ $pcm$.

%The results demonstrate whole-core runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and statistical error in $k_{eff}$ of $\leq$ $25$ $pcm$.
%
%Simulations consisted in 500 active cycles of 2∙104 neutrons. 20 inactive cycles were used for the convergence of the
%fission source distribution.
%
%Each simulation in this study skipped 200 generations before beginning active tallies to ensure fission source convergence.
%
%In order to minimize statistical errors and assure reliable fission source convergence, up to 2000 active fission source iteration cycles with 150,000 histories per cycle were used in neutron transport calculations with MCNP
%
%The MCNP transport step within the VESTA simulation uses 300 active cycles, 50 inactive cycles,
%and 100,000 particles per cycl
%
%The fission source defined in Serpent Code automatically dis-
%tributes the initial guess in fuel zones, with enhances the overall performance. Besides, the number of histories was selected to get the intended statistical convergence, considering the computa- tional effort involved. Accordingly, the following scheme was selected:
%? A Source with v3 ? 108 histories was selected for all cases where CRW is calculated in order to reach a statistical uncer- tainty of v5 pcm at 1 r for each calculation and a final value of CRW uncertainty below 5%.
%? A Source with v2 ? 107 histories was selected for all burnup cases in order to reach a statistical uncertainty of v20 pcm at 1 r for each calculation.
%3.3.
%
%The results presented in the following were obtained after full-core calculations simulating 250 million active neutron histories with the version 1.1.16 of the code. Simulations consisted in 500 active cycles of 5∙105 neutrons subdivided in 16 parallel tasks. Seventy inactive cycles were adopted to allow for the convergence of the fission source distribution. Convergence has been checked through the fission source entropy. Results

@@

The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.

@@

The shutdown margin (SDM) is the amount of reactivity by which a full reactor core is subcritical from a given state. The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient negative reactivity. The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity:

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod impacts the reactivity worth of another control rod in 
the surroundings. 
The insertion of a CR depresses the neutron flux
in its vicinity and makes the curvature of the neutron flux greater. The gradient
of the neutron flux will contrarily increase at a radial distance. The CRs, distributed in the core,
will distort the neutron flux around each other and will impact the reactivity worth.
The term ``shadowing effect" has been used to describe this \cite{oka2014nuclear}.
The shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D), CR locations, and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear}.

The amplification factor of the i$^{th}$ CR (A$_{CRi}$) helps to evaluate the shadowing effects between CR clusters. The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:
